### 2020-03-17 README.Rmd
attempt to correct visualization error (should pass tests and "visually" look correct). Still not correct...

df_groups %>% ggplot(aes(x = S, y = I, z = R, group = sim)) +
    geom_line(alpha = .1) +
    coord_tern()
```

>>>>

df_groups %>% ggplot() +
    geom_prediction_band(aes(x = S, y = I, z = R, sim_group = as.numeric(sim)),
                         alpha = .2, fill = "blue", color = "blue") +
    geom_line(aes(x = S, y = I, z = R, group = sim), alpha = .1) +
    coord_tern()
```
